---
title: "Master Thesis Project PN - Manipulation Effects"
author: "Paula Neubauer"
date: "2025-07-31"
output:
  github_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# REQUIRED PACKAGES
require(performance) # marginal + conditional R2
require(lme4) # linear-mixed-effects models
require(lmerTest, warn.conflicts = FALSE) # linear-mixed-effects models
require(emmeans, warn.conflicts = FALSE) # estimated marginal means (EMMs)
require(ggplot2, warn.conflicts = FALSE) # creating graphs
require(dplyr, warn.conflicts = FALSE) # for %>% operator
library(ggpubr, warn.conflicts = FALSE) # ggscatter()-function
library(knitr) # dynamic report generation
library(kableExtra) # table formatting
library(stringr) # for string modifications
library(tidyverse)
library(simr)
library(gridExtra) # arrange ggplots
library(ggpubr) # get legend of ggplots
library(WeightIt)
library(cobalt)
library(robustlmm)
library(psych)
library(car)

#df_trial <- readRDS("C:/Users/Paula_Neubauer/Desktop/manipulation_analysis_PN/df_trial_15.rds")
df_grip <- readRDS("C:/Users/Paula_Neubauer/Desktop/manipulation_analysis_PN/df_grip.rds")
#df_trial_groups <- readRDS("C:/Users/Paula_Neubauer/Desktop/manipulation_analysis_PN/df_et_with_group.rds")
```

```{r}
df_grip <- df_grip %>%
  filter(id != "19102022")
```

# Subject Level #
## distribution of dependent variables
```{r}
df_grip <- df_grip %>%
  group_by(id) %>%
  mutate(
    z_rpd = (rpd - mean(rpd, na.rm = TRUE)) / sd(rpd, na.rm = TRUE)
  ) %>%
  ungroup()

df_grip <- df_grip %>%
  group_by(id) %>%
  mutate(
    z_rpd_low = (rpd_low - mean(rpd_low, na.rm = TRUE)) / sd(rpd_low, na.rm = TRUE)
  ) %>%
  ungroup()

df_grip$z_rpd <- as.numeric(df_grip$z_rpd)

par(mfrow = c(3,2), mar = c(4, 4, 2, 1))
hist(df_grip$z_rpd,
     main = "Distribution of z_rpd (500-1500 ms)",
     xlab = "rpd)",
     breaks = 200)
hist(df_grip$z_rpd_low,
     main = "Distribution of z_rpd_low (0-250 ms)",
     xlab = "rpd_low",
     xlim = c(-4, 6),
     breaks = 200)
hist(df_grip$trial_corr_rpd,
     main = "Distribution of Trial Corrected RPD",
     xlab = "Trial Corrected RPD",
     xlim = c(-1.4, 1.7),  
     breaks = 200)          

```

## Sample
```{r}
# New data frame: 1 row per subject containing sample description data (consistent across conditions)
sample_description_df <- df_grip %>%
  group_by(id) %>%
  summarise(across(everything(), ~ {
    vals <- na.omit(.x) # removes NAs so we only check actual values
    # keeps the column if all non-NA values are identical + returns that consistent value (or NA if all were NA)
    if (length(unique(vals)) <= 1) unique(vals)[1] else NA 
  }), .groups = "drop") %>% 
  # Keep columns that have at least some non-NA values + removes columns that are completely NA across all subjects
  select(where(~ any(!is.na(.))))
sample_description_df$block_baseline_mean <- NULL
```

```{r}
# Sample size
nrow(sample_description_df)
table(sample_description_df$group.y)
```

## Sample Description
```{r}
# Function returning group mean + sd
fun_return_descriptives <- function(group){
  group_df <- sample_description_df[
    sample_description_df$group.y == group,
    c("gender", "age", "CBCL", "YSR","z_grip_strength", "id",
      "verbal_IQ", "non_verbal_IQ")] 
  # gender
  n <- length(unique(group_df$id))
  male <- (length(which(group_df$gender == "männlich")))
  female <- (length(which(group_df$gender == "weiblich")))
  gender_f_m <- paste(female,"/",male)
  # age
  age_mean <- round(mean(group_df$age, na.rm = TRUE), digits = 1)
  age_sd <- round(sd(group_df$age, na.rm = TRUE), digits = 1)
  age <- paste(age_mean, "(",age_sd,")" )
  # grip strength
  grip_strength_mean <- round(mean(group_df$z_grip_strength, na.rm = TRUE), digits = 1)
  grip_strength_sd <- round(sd(group_df$z_grip_strength, na.rm = TRUE), digits = 1)
  grip_strength <- paste(grip_strength_mean, "(", grip_strength_sd, ")")
  # verbal IQ
  verbal_IQ_mean <- round(mean(group_df$verbal_IQ, na.rm = TRUE), digits = 1)
  verbal_IQ_sd <- round(sd(group_df$verbal_IQ, na.rm = TRUE), digits = 1)
  verbal_IQ <- paste(verbal_IQ_mean, "(", verbal_IQ_sd, ")")
  # non-verbal IQ
  non_verbal_IQ_mean <- round(mean(group_df$non_verbal_IQ, na.rm = TRUE), digits = 1)
  non_verbal_IQ_sd <- round(sd(group_df$non_verbal_IQ, na.rm = TRUE), digits = 1)
  non_verbal_IQ <- paste(non_verbal_IQ_mean, "(", non_verbal_IQ_sd, ")")

  
  group_description <- data.frame(
    n,
    gender_f_m,
    age,
    verbal_IQ,
    non_verbal_IQ,
    grip_strength)
  t(group_description)
}

asd_description <- fun_return_descriptives(group = "ASD")
colnames(asd_description) <- "ASD"
con_description <- fun_return_descriptives(group = "CON")
colnames(con_description) <- "CON"
mhc_description <- fun_return_descriptives(group = "MHC")
colnames(mhc_description) <- "MHC"
```

```{r}
## p-values for descriptive statistics
age_anova <- aov(age ~ group.y, data = sample_description_df)
age_anova_p <- summary(age_anova)[[1]][["Pr(>F)"]][[1]]
grip_strength_anova <- aov(z_grip_strength ~ group.y, data = sample_description_df)
grip_strength_anova_p <- summary(grip_strength_anova)[[1]][["Pr(>F)"]][[1]]
verbal_IQ_anova <- aov(verbal_IQ ~ group.y, data = sample_description_df)
verbal_IQ_anova_p <- summary(verbal_IQ_anova)[[1]][["Pr(>F)"]][[1]]
non_verbal_IQ_anova <- aov(non_verbal_IQ ~ group.y, data = sample_description_df)
non_verbal_IQ_anova_p <- summary(non_verbal_IQ_anova)[[1]][["Pr(>F)"]][[1]]
gender_chi2 <- chisq.test(sample_description_df$gender, sample_description_df$group.y)
gender_chi2_p <- gender_chi2$p.value

p_values <- c(
  NA,
  gender_chi2_p,
  age_anova_p,
  grip_strength_anova_p,
  verbal_IQ_anova_p,
  non_verbal_IQ_anova_p)

p_value <- sapply(p_values, function(p) {
  if (is.na(p)) {
    NA
  } else if (p < 0.001) {
    "< 0.001"
  } else {
    format(p, scientific = F)
    round(p, 3)
  }
})

sample_table <- cbind(asd_description, con_description, mhc_description, p_value)
# Redo table row and column names
rownames(sample_table)[rownames(sample_table) == "grip_strength"] <- "grip strength [z]"
rownames(sample_table)[rownames(sample_table) == "gender_f_m"] <- "gender (f/m)"
rownames(sample_table)[rownames(sample_table) == "verbal_IQ"] <- "verbal IQ"
rownames(sample_table)[rownames(sample_table) == "non_verbal_IQ"] <- "non verbal IQ"
colnames(sample_table)[colnames(sample_table) == "p_value"] <- "p value"

sample_description_table <- knitr::kable(sample_table,
                                         caption = "Sample description",
                                         digits = 4,
                                         align = "c")
sample_description_table
```


```{r}
# Grip strength
# 1. Descriptive statistics
sample_table <- df_grip %>%
  group_by(group.y) %>%
  summarise(
    N = n(),
    Mean = mean(grip_strength.y, na.rm = TRUE),
    SD = sd(grip_strength.y, na.rm = TRUE)
  )

# 2. Run ANOVA
anova_result <- aov(grip_strength.y ~ group.y, data = df_grip)
p_val <- summary(anova_result)[[1]][["Pr(>F)"]][1]

# 3. Format caption with p-value
caption_text <- paste0("Descriptive statistics for grip strength by group (ANOVA p = ",
                       formatC(p_val, format = "f", digits = 4), ")")

sample_description_table <- knitr::kable(sample_table,
                                         caption = caption_text,
                                         digits = 4,
                                         align = "c")

# Print table
sample_description_table
```


## Plots 
```{r}
## Plot: Age
ggplot(sample_description_df, aes(x = group.y, y = age), col = group.y) +
  geom_boxplot(fill = "grey") +
  geom_jitter() +
  geom_signif(comparisons = list(c("ASD", "CON"), c("ASD", "MHC"), c("MHC", "CON")),
              map_signif_level=TRUE,
              y_position = c(19.5, 20, 19)) +
  theme_bw() + 
  theme_classic() +
  ggtitle("Age") +
  theme(plot.title = element_text(face="bold"))

## Plot: IQ-verbal
plot_verbal_iq <- ggplot(sample_description_df, aes(x = group.y, y = verbal_IQ), col = group.y) + 
  geom_boxplot(fill = "grey") +
  geom_signif(comparisons = list(c("ASD", "CON"), c("ASD", "MHC"), c("MHC", "CON")),
              map_signif_level=TRUE,
              y_position = c(135, 140, 130)) +
  theme_bw() + 
  theme_classic() +
  ggtitle("IQ-verbal") +
  theme(plot.title = element_text(face="bold")) +
  theme(plot.margin = unit(c(1, 0.5, 0.5, 0.5), "cm"))

## Plot: IQ-non-verbal
plot_non_verbal_iq <- ggplot(sample_description_df, aes(x = group.y, y = non_verbal_IQ), col = "group.y") + 
  geom_boxplot(fill = "grey") +
  geom_signif(comparisons = list(c("ASD", "CON"), c("ASD", "MHC"), c("MHC", "CON")),
              map_signif_level=TRUE,
              y_position = c(135, 140, 130)) +
  theme_bw() + 
  theme_classic() +
  ggtitle("IQ-non-verbal") +
  theme(plot.title = element_text(face="bold")) +
  theme(plot.margin = unit(c(1, 0.5, 0.5, 0.5), "cm"))
  
grid.arrange(plot_verbal_iq, plot_non_verbal_iq, ncol = 2)
```


```{r}
hist(df_grip$trial_corr_rpd, main = "Histogram of Trial Corrected RPD", xlab = "Trial Corrected RPD", col = "lightblue", border = "black")
```


```{r}
# Compute descriptive stats
mean_value <- mean(df_grip$trial_corr_rpd, na.rm = TRUE)
sd_value <- sd(df_grip$trial_corr_rpd, na.rm = TRUE)
median_value <- median(df_grip$trial_corr_rpd, na.rm = TRUE)
min_value <- min(df_grip$trial_corr_rpd, na.rm = TRUE)
max_value <- max(df_grip$trial_corr_rpd, na.rm = TRUE)

# Create a table
descriptives <- data.frame(
  Statistic = c("Mean", "Standard Deviation", "Median", "Min", "Max"),
  Value = round(c(mean_value, sd_value, median_value, min_value, max_value), 3)
)

# Show as table
knitr::kable(descriptives, caption = "Descriptive Statistics for trial_corr_rpd")
```


## Covariate Check 
```{r}
# gender as a factor
df_grip$gender <- as.factor(df_grip$gender)

# Fit a mixed model with covariates
lmm_covariates <- lmer(trial_corr_rpd ~ verbal_IQ + non_verbal_IQ + age + gender + grip_strength.y + (1|id), data = df_grip, REML = FALSE)
anova_table <- anova(lmm_covariates)
knitr::kable(anova_table, caption = "ANOVA Results")
```

## Linear Mixed-Effects Model: Effect of Experimental Manipulation
```{r}
# Result 1:
df_grip$trial_phase <- factor(
  df_grip$trial_phase,
  levels = c("baseline_pre_squeeze", "squeeze", "baseline_post_squeeze", "relax")
)

lmm_baseline <- lmer(
  trial_corr_rpd ~ trial_phase + (1 | id),
  data = df_grip
)
anova_table <- anova(lmm_baseline)
knitr::kable(anova_table, caption = "ANOVA Results")
r2_nakagawa(lmm_baseline)  
```

```{r}
# Compute estimated marginal means
emm_result <- emmeans(lmm_baseline, ~ trial_phase)

# Display the EMMs as a clean markdown table
knitr::kable(emm_result, caption = "Estimated Marginal Means by Trial Phase")
```

### Post Hoc
```{r}
# Compute pairwise contrasts
emm_result <- emmeans(lmm_baseline, ~ trial_phase)
pairwise_contrasts <- contrast(emm_result, "pairwise")

# Display the contrasts
knitr::kable(pairwise_contrasts, caption = "Pairwise Comparisons Between Trial Phases")

# Compute and display confidence intervals for the contrasts
pairwise_contrasts_ci <- confint(pairwise_contrasts)
knitr::kable(pairwise_contrasts_ci, caption = "95% Confidence Intervals for Pairwise Comparisons")
```

```{r}
emmeans_result <- emmeans(lmm_baseline, ~ trial_phase)  
plot_data <- as.data.frame(emmeans_result)

# Ensure correct order of trial phases
plot_data$trial_phase <- factor(
  plot_data$trial_phase,
  levels = c("baseline_pre_squeeze", "squeeze", "baseline_post_squeeze", "relax")
)

# plot
emm_plot <- ggplot(plot_data) +
  geom_crossbar(aes(
    x = trial_phase, y = emmean,
    ymin = emmean - SE, ymax = emmean + SE),
    fill = "gray70", color = "black",
    width = 0.3, alpha = 0.8) +
  geom_errorbar(aes(
    x = trial_phase, ymin = lower.CL, ymax = upper.CL),
    width = 0.2, color = "black") +
  scale_x_discrete(labels = c(
    "baseline_pre_squeeze" = "Baseline Pre Grip",
    "squeeze" = "Grip",
    "baseline_post_squeeze" = "Baseline Post Grip",
    "relax" = "Relax"
  )) +
  theme_bw() +
  labs(
    title = "Estimated Marginal Pupil Response by Trial Phase",
    x = "Trial Phase",
    y = "Estimated Marginal Pupil Response"
  ) +
  theme(
    plot.title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

# Display plot
print(emm_plot)

```

### Effort Check: Grip strength 
```{r}
df_grip %>%
  filter(trial_phase == "squeeze") %>%
  summarise(
    mean_grip = mean(grip_strength.y, na.rm = TRUE),
    sd_grip = sd(grip_strength.y, na.rm = TRUE)
  )
```

```{r}
lmm_grip <- lmer(trial_corr_rpd ~ grip_strength.y + (1 | id),
              data = df_grip)
anova_table <- anova(lmm_grip)
knitr::kable(anova_table, caption = "ANOVA Results")
```

```{r}
lmm_gripstrength <- lmer(
  trial_corr_rpd ~ trial_phase * grip_strength.y + (1 | id),
  data = df_grip 
)
anova(lmm_gripstrength)
knitr::kable(anova_table, caption = "ANOVA Results")
```

```{r}
# Compute estimated marginal trends of grip_strength.y by trial phase
trend_result <- emtrends(
  lmm_gripstrength,
  ~ trial_phase,
  var = "grip_strength.y",
  infer = c(TRUE, TRUE)
)

# Display as Markdown table
knitr::kable(trend_result, caption = "Estimated Slopes of Grip Strength by Trial Phase")
```

## Group differences
```{r}
# Result 2:
# Ensure group is treated as factor
df_grip$group.y <- as.factor(df_grip$group.y)

# Fit model
lmm_group <- lmer(
  trial_corr_rpd ~ trial_phase * group.y + (1 | id),
  data = df_grip
)

# Run and display ANOVA table
anova_table <- anova(lmm_group)
knitr::kable(anova_table, caption = "ANOVA Results")

# Compute and display marginal and conditional R²
r2_values <- r2_nakagawa(lmm_group)
knitr::kable(r2_values, caption = "Nakagawa R² for Mixed Model")
```

```{r}
# Compute estimated marginal means of group within each trial phase
emm_group_trial <- emmeans(lmm_group, ~ group.y | trial_phase)

# Display as markdown table
knitr::kable(emm_group_trial, caption = "Estimated Marginal Means: Group within Trial Phase")
```

### Post Hoc
```{r}
# pairwise phase comparison within each group (not about group differences)
contrast(emmeans(lmm_group, ~ trial_phase | group.y), "pairwise")
confint(contrast(emmeans(lmm_group, ~ trial_phase | group.y), "pairwise"))
```

```{r}
# Compute estimated marginal means of group within each trial phase
emm_group_trial <- emmeans(lmm_group, ~ group.y | trial_phase)

# Compute pairwise group comparisons within each trial phase
group_comparisons <- contrast(emm_group_trial, "pairwise")
knitr::kable(group_comparisons, caption = "Pairwise Group Comparisons within Trial Phase")

# Confidence intervals for the pairwise comparisons
group_comparisons_ci <- confint(group_comparisons)
knitr::kable(group_comparisons_ci, caption = "95% Confidence Intervals for Pairwise Group Comparisons")
```


```{r}
# Compute estimated marginal means
emm_result <- emmeans(lmm_group, ~ group.y | trial_phase)
emm_data <- as.data.frame(emm_result)

# Ensure correct phase order
emm_data$trial_phase <- factor(
  emm_data$trial_phase,
  levels = c("baseline_pre_squeeze", "squeeze", "baseline_post_squeeze", "relax")
)

# Plot estimated marginal means with confidence intervals
ggplot(emm_data, aes(x = trial_phase, y = emmean, color = group.y)) +
  geom_point(size = 3, position = position_dodge(width = 0.5)) +
  geom_errorbar(
    aes(ymin = lower.CL, ymax = upper.CL),
    width = 0.2,
    size = 1,
    position = position_dodge(width = 0.5)
  ) +
  facet_wrap(~ group.y) +
  scale_x_discrete(labels = c(
    "baseline_pre_squeeze" = "Baseline Pre Grip",
    "squeeze" = "Grip",
    "baseline_post_squeeze" = "Baseline Post Grip",
    "relax" = "Relax"
  )) +
  labs(
    title = "Estimated Marginal Pupil Response by Group and Trial Phase",
    x = "Trial Phase",
    y = "Estimated Marginal Pupil Response"
  ) +
  theme_bw() +
  scale_color_manual(values = c("ASD" = "red", "CON" = "#045D5D", "MHC" = "#A05000")) +
  theme(
    plot.title = element_text(face = "bold"),
    legend.position = "none",
    axis.text.x = element_text(face = "bold", angle = 45, hjust = 1),
    axis.text.y = element_text(face = "bold"),
    text = element_text(size = 14)
  )

```

```{r}
# Plot estimated marginal means by phase (facets), color = group
ggplot(emm_data, aes(x = group.y, y = emmean, color = group.y)) +
  geom_point(size = 3, position = position_dodge(width = 0.5)) +
  geom_errorbar(
    aes(ymin = lower.CL, ymax = upper.CL),
    width = 0.2,
    size = 1,
    position = position_dodge(width = 0.5)
  ) +
  facet_wrap(~ trial_phase) +
  scale_color_manual(values = c(
    "ASD" = "#9900CC",   # bright purple
    "CON" = "#00FF00",   # bright green
    "MHC" = "#00FFFF"    # bright cyan
  )) +
  labs(
    title = "Estimated Marginal Pupil Response by Trial Phase and Group",
    x = "Group",
    y = "Estimated Marginal Pupil Response"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold"),
    legend.position = "none",
    axis.text.x = element_text(face = "bold"),
    axis.text.y = element_text(face = "bold"),
    text = element_text(size = 14)
  )

```


## Across Manipulation trials - Habituation Effects
```{r}
# Result 3:
# Ensure manipulation_trial is a factor
df_grip$manipulation_trial <- as.factor(df_grip$manipulation_trial)

# Fit mixed-effects model
lmm_trials <- lmer(
  trial_corr_rpd ~ manipulation_trial * trial_phase + (1 | id),
  data = df_grip
)

# Run and display ANOVA table
anova_table <- anova(lmm_trials)
knitr::kable(anova_table, caption = "ANOVA Results for Manipulation Trial × Trial Phase")

# Compute and display marginal/conditional R²
r2_trials <- r2_nakagawa(lmm_trials)
knitr::kable(r2_trials, caption = "Nakagawa R² for Manipulation Trial Model")
```

### Post Hoc
```{r}
# Compute estimated marginal means of trial_phase within each manipulation trial
emm_phase_within_trial <- emmeans(lmm_trials, ~ trial_phase | manipulation_trial)

# Compute pairwise comparisons
phase_comparisons <- contrast(emm_phase_within_trial, "pairwise")
knitr::kable(phase_comparisons, caption = "Pairwise Comparisons: Trial Phase within Manipulation Trial")

# Compute and display confidence intervals
phase_comparisons_ci <- confint(phase_comparisons)
knitr::kable(phase_comparisons_ci, caption = "95% CIs for Trial Phase Comparisons within Manipulation Trial")
```

```{r}
# Get estimated marginal means
emms <- emmeans(lmm_trials, ~ trial_phase | manipulation_trial)

# Convert to a dataframe
emms_df <- as.data.frame(emms)

# Relabel trial_phase and manipulation_trial
emms_df <- emms_df %>%
  mutate(
    trial_phase = factor(trial_phase,
                         levels = c("baseline_pre_squeeze", "squeeze", "baseline_post_squeeze", "relax"),
                         labels = c("Baseline Pre-Grip", "Grip", "Baseline Post-Grip", "Relax")),
    trial = as.numeric(as.character(manipulation_trial))
  )

# Plot
ggplot(emms_df, aes(x = trial, 
                    y = emmean, 
                    color = trial_phase,
                    group = trial_phase)) +
  geom_line(size = 1.2) +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 0.1) +
  labs(
    title = "Estimated Marginal Means of RPD by Trial Phase and Trial",
    x = "Trial",
    y = "Estimated Relative Pupil Dilation (RPD)",
    color = "Trial Phase"
  ) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "right")
```


```{r}
# Compute estimated marginal means of manipulation_trial within each trial phase
emm_trial_within_phase <- emmeans(lmm_trials, ~ manipulation_trial | trial_phase)

# Pairwise comparisons of manipulation_trial within each phase
trial_comparisons <- contrast(emm_trial_within_phase, "pairwise")
knitr::kable(trial_comparisons, caption = "Pairwise Comparisons: Manipulation Trial within Trial Phase")

# Confidence intervals for those comparisons
trial_comparisons_ci <- confint(trial_comparisons)
knitr::kable(trial_comparisons_ci, caption = "95% CIs for Manipulation Trial Comparisons within Trial Phase")
```


```{r}
# Get EMMs by trial_phase within each manipulation_trial
emm_data <- emmip(
  lmm_trials,
  ~ trial_phase | manipulation_trial,
  CIs = TRUE,
  plotit = FALSE
)

# Ensure trial phase order
emm_data$trial_phase <- factor(
  emm_data$trial_phase,
  levels = c("baseline_pre_squeeze", "squeeze", "baseline_post_squeeze", "relax")
)

# Plot
ggplot(emm_data, aes(x = trial_phase, y = yvar, color = as.factor(manipulation_trial), group = manipulation_trial)) +
  geom_point(size = 2) +
  geom_line(size = 1) +
  #geom_errorbar(aes(ymin = LCL, ymax = UCL), width = 0.2) +
  labs(
    title = "Effect of Trial Phase on Pupil Response by Manipulation Trial",
    x = "Trial Phase",
    y = "Estimated Marginal Pupil Response",
    color = "Manipulation Trial"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    text = element_text(size = 14)
  )
```

## Across Manipulation trials with groups - Habituation Effects
```{r}
# Result 4
# Fit model with group × manipulation_trial × trial_phase interaction
lmm_trials_group <- lmer(
  trial_corr_rpd ~ group.y * manipulation_trial * trial_phase + (1 | id),
  data = df_grip
)

# Run and display ANOVA table
anova_table <- anova(lmm_trials_group)
knitr::kable(anova_table, caption = "ANOVA Results: Group × Trial × Phase Interaction")

# Compute and display marginal/conditional R²
r2_group_trials <- r2_nakagawa(lmm_trials_group)
knitr::kable(r2_group_trials, caption = "Nakagawa R² for Group × Manipulation Trial × Phase Model")
```

```{r}
# Compute estimated marginal means of trial_phase within each group × manipulation trial combination
emm_group_trial_phase <- emmeans(lmm_trials_group, ~ trial_phase | group.y * manipulation_trial)

# Display the results as a Markdown table
knitr::kable(emm_group_trial_phase, caption = "Estimated Marginal Means: Trial Phase by Group and Manipulation Trial")
```

### Post Hoc
```{r}
# Compute EMMs for trial_phase within each group × manipulation_trial
emm_nested <- emmeans(lmm_trials_group, ~ trial_phase | group.y * manipulation_trial)

# Pairwise contrasts
nested_contrasts <- contrast(emm_nested, "pairwise")
knitr::kable(nested_contrasts, caption = "Pairwise Comparisons: Trial Phase by Group × Manipulation Trial")

# Confidence intervals for those contrasts
nested_contrasts_ci <- confint(nested_contrasts)
knitr::kable(nested_contrasts_ci, caption = "95% CIs for Trial Phase Comparisons by Group × Manipulation Trial")
```

```{r}
# Get estimated marginal means for the interaction
emm_data <- emmip(
  lmm_trials_group,
  ~ trial_phase | group.y * manipulation_trial,
  CIs = TRUE,
  plotit = FALSE
)

# Ensure correct order of trial phases
emm_data$trial_phase <- factor(
  emm_data$trial_phase,
  levels = c("baseline_pre_squeeze", "squeeze", "baseline_post_squeeze", "relax")
)

# Plot
ggplot(emm_data, aes(x = trial_phase, y = yvar, group = manipulation_trial, color = as.factor(manipulation_trial))) +
  geom_point(size = 2) +
  geom_line(size = 1) +
  #geom_errorbar(aes(ymin = LCL, ymax = UCL), width = 0.2) +
  facet_wrap(~ group.y) +
  scale_x_discrete(labels = c(
    "baseline_pre_squeeze" = "Baseline Pre Grip",
    "squeeze" = "Grip",
    "baseline_post_squeeze" = "Baseline Post Grip",
    "relax" = "Relax"
  )) +
  labs(
    title = "Group × Manipulation Trial × Phase Interaction on Pupil Response",
    x = "Trial Phase",
    y = "Estimated Marginal Pupil Response",
    color = "Manipulation Trial"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    text = element_text(size = 14)
  )
```

## Assumption checks
### Baseline model - Effect of Experimental Manipulation
```{r}
check_model(lmm_baseline)
performance::check_model(lmm_baseline)
```

### Group
```{r}
check_model(lmm_group)
performance::check_model(lmm_group)
```

### Across trials - Habituation effects
```{r}
check_model(lmm_trials)
performance::check_model(lmm_trials)
```

### Habituation effects with groups
```{r}
check_model(lmm_trials_group)
performance::check_model(lmm_trials_group)
```




